HERMES : Hybrid ERror-corrector Model with inclusion of External Signals for nonstationary fashion time series

### 2021-12-02 hermes_paper/hermes_paper.tex
Correction section 2

At this stage, we want to train a global RNN, trained on all the N sequences and able to understand and correct the weaknesses of the first per-time-series parametric models. This task requires a thorough data pre-processing for two main reasons. Firstly, we want to give to the RNN the best input in order to understand the initial collection of forecasts and predict their future errors. Secondly, as we did not suppose any assumption about the scale of our time series, we have to carefully normalize them before feeding our RNN with.
In this way, we define the following pre-processing :
%At this stage, we can write that for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
%$$
%\ts^n_{T+i} = \tspred^{stat,n}_{T+i|T} + \varepsilon^n_{T+i}\,,
%$$
%In this paper, we introduce a model based on a latent regime. In regime 0, the first parametric forecast succeeds at catching all the information of the $n$-th sequence and the final forecast of our framework is the prediction of the per-time-series parametric model. Conversely, in regime 1, the first parametric forecast is unaccurate and it remains a residual random error term that can be estimated. % quantity that we note $\remainder$. 
%Conditionally on $\{\fullts^n\}_{1\leqslant n\leqslant N}$, our regime-switching model is:

@@

Let $\window \in \mathbb{N}$ be the window size, usually this window is proportional to the forecast horizon $\window \propto \lag$. We define as our RNN input the following  normalized, deseasonalized and rescaled sequence $\rnnwindow^n_T = \{\rnninput^{n}_{T-\window+i|T}\}_{1\leqslant i \leqslant w}$, where, for all $1\leqslant n \leqslant N$ and $1\leqslant i \leqslant w$, 
$$
\rnninput^{n,T}_{T-w+i|T} = \frac{\ts^n_{T-w+i} -\tspred^{pred,n}_{T+i|T}}{\meants^n_T}\,,
$$
where $ \meants^n_T = \frac{1}{w}\sum_{i = 1}^{w}\ts^n_{T-w+i}$.

We note $\rnn(.;\rnnparam)$ the recurrent neural network model where $\rnnparam$ are  unknown parameters. Given the RNN input sequences $\{\rnnwindow^n_T\}_{1\leqslant n \leqslant N}$ and the global RNN estimated parameters $\{\rnnparam\}$, the error-corrector predictions $\{\tspred^{corr,n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ are, for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
$$
\tspred^{corr,n}_{T+i|T} = \rnn(\rnnwindow^n_T;\rnnparam)_i \cdot \meants^n_T\ \,.
$$

@@

Using well-fitted time-series-specific parametric models, our hybrid network corrects the first form of weakness and achieves striking accuracy on our dataset. Then, for the second form of weakness, the shared recurrent neural network relies on the strength of machine learning methods at leveraging a huge quantities of heterogeneous data.
In addition to the $N$ target time series, we consider $K \times N$ external sequences indexed from $0$ to $T$. For all $1\leqslant n \leqslant N$, $1\leqslant k \leqslant K$ and  $1\leqslant t \leqslant T$, let $\ws^{n,k}_t$ be the value of the $k$-th external sequence at time $t$ linked to the sequence $\fullts^n$. We note $\fullws^n = \{\{\ws_t^{n,k}\}_{1\leqslant t \leqslant T}\}_{1\leqslant k \leqslant K}$ all the values of the family of weak signals linked to the $n$-th sequence. In addition, let $\fullws^n_T = \{\{\ws_{T-w+i}^{n,k}\}_{1\leqslant i \leqslant \window}\}_{1\leqslant k \leqslant K}$ be only the last $\window$ terms of the family. Concatenating $ \rnnwindow^n_T$ and $\fullws^n_T$, we define a new input for our RNN,   
$$
\fullconcatinput^n_T = \{\concatinput^n_{T-w+i|T}\}_{1\leqslant i \leqslant w}= \{\rnninput^n_{T-w+i|T}, \ws^{n,1}_{T-w+i},...,\ws^{n,K}_{T-w+i}\}_{1\leqslant i \leqslant w}\,.
$$
Finally, for all $1\leqslant n \leqslant N$ and for all $i \in \{1,\ldots,\lag\}$ our final model becomes:
%$$
%\tspred^n_{T+i|T} 
%= \etspred^{ets,n}_{T+i|T} +  \rnnmodel(\fullconcatinput^n_T)_{T+i} \times \meants^n_T
%$$
\begin{equation}
\label{eq:withws:full:model}
\tspred^n_{T+i|T}  = \tspred^{pred,n}_{T+i|T} +  \tspred^{corr,n}_{T+i|T} = \stat^n(\ts^n_{1:T};\statparam^n)_i +  \rnn(\fullconcatinput^n_T;\rnnparam)_i \cdot \meants^n_T\
\end{equation}

>>>>

The second part of our model is a global RNN, trained on all the $N$ sequences to correct the weaknesses of the first per-time-series parametric models. This task requires a thorough data pre-processing for two main reasons. First, we provide  to the RNN the best input in order to understand the initial collection of forecasts and predict their future errors. Second, as we did not make any assumption about the scale of our time series, we have to carefully normalize them before feeding them to the RNN.
Consider the following pre-processing. 
%At this stage, we can write that for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
%$$
%\ts^n_{T+i} = \tspred^{stat,n}_{T+i|T} + \varepsilon^n_{T+i}\,,
%$$
%In this paper, we introduce a model based on a latent regime. In regime 0, the first parametric forecast succeeds at catching all the information of the $n$-th sequence and the final forecast of our framework is the prediction of the per-time-series parametric model. Conversely, in regime 1, the first parametric forecast is unaccurate and it remains a residual random error term that can be estimated. % quantity that we note $\remainder$. 
%Conditionally on $\{\fullts^n\}_{1\leqslant n\leqslant N}$, our regime-switching model is:

@@

Let $\window \in \mathbb{N}$ be the window size, usually this window is proportional to the forecast horizon $\window \propto \lag$. We define as our RNN input the following  normalized, deseasonalized and rescaled sequence $\rnnwindow^n_T = \{\rnninput^{n}_{T-\window+i|T}\}_{1\leqslant i \leqslant w}$, where, for all $1\leqslant n \leqslant N$ and $1\leqslant i \leqslant w$, 
$$
\rnninput^{n,T}_{T-w+i|T} = \frac{\ts^n_{T-w+i} -\tspred^{pred,n}_{T+i|T}}{\meants^n_T}\,,\quad\mbox{where}\quad \meants^n_T = \frac{1}{w}\sum_{i = 1}^{w}\ts^n_{T-w+i}\,.
$$

We note $\rnn(.;\rnnparam)$ the recurrent neural network model where $\rnnparam$ are  unknown parameters. Given the RNN input sequences $\{\rnnwindow^n_T\}_{1\leqslant n \leqslant N}$ and the global RNN estimated parameters $\rnnparam$, the error-corrector predictions $\{\tspred^{corr,n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ are, for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
$$
\tspred^{corr,n}_{T+i|T} = \rnn(\rnnwindow^n_T;\rnnparam)_i \cdot \meants^n_T\ \,.
$$

@@

Using well-fitted time-series-specific parametric models, our hybrid network corrects the first form of weakness and achieves striking accuracy on our dataset, \textcolor{red}{see Table~XXX}. Then, to correct the second form of weakness, in addition to the $N$ target time series, we consider $K \times N$ external sequences indexed from $0$ to $T$. For all $1\leqslant n \leqslant N$, $1\leqslant k \leqslant K$ and  $1\leqslant t \leqslant T$, let $\ws^{n,k}_t$ be the value of the $k$-th external sequence at time $t$ linked to the sequence $\fullts^n$. We note $\fullws^n = \{\{\ws_t^{n,k}\}_{1\leqslant t \leqslant T}\}_{1\leqslant k \leqslant K}$ all the values of the family of weak signals linked to the $n$-th sequence. In addition, let $\fullws^n_T = \{\{\ws_{T-w+i}^{n,k}\}_{1\leqslant i \leqslant \window}\}_{1\leqslant k \leqslant K}$ be only the last $\window$ terms of the family. Concatenating $ \rnnwindow^n_T$ and $\fullws^n_T$, we define a new input for our RNN,   
$$
\fullconcatinput^n_T = \{\concatinput^n_{T-w+i|T}\}_{1\leqslant i \leqslant w}= \{\rnninput^n_{T-w+i|T}, \ws^{n,1}_{T-w+i},...,\ws^{n,K}_{T-w+i}\}_{1\leqslant i \leqslant w}\,.
$$
Finally, for all $1\leqslant n \leqslant N$ and for all $i \in \{1,\ldots,\lag\}$ our final model becomes:
%$$
%\tspred^n_{T+i|T} 
%= \etspred^{ets,n}_{T+i|T} +  \rnnmodel(\fullconcatinput^n_T)_{T+i} \times \meants^n_T
%$$
\begin{equation}
\label{eq:withws:full:model}
\tspred^n_{T+i|T}  = \tspred^{pred,n}_{T+i|T} +  \tspred^{corr,n}_{T+i|T} = \stat^n(\ts^n_{1:T};\statparam^n)_i +  \rnn(\fullconcatinput^n_T;\rnnparam)_i \cdot \meants^n_T\
\end{equation}
